Think deep for reef resilience

### 2025-09-25 paper/paper_draft.qmd
Objective writing style and remove repetition of "exploratory modelling"

We adapted an exploratory scenario modelling approach for this investigation. Specifically,
we use combinations of model factors to investigate a wide range of potential futures under
different assumptions of environmental (climatic) and ecological conditions. Exploratory
modelling approaches have gained favour in recent years to explore the implications of deep
uncertainty; where there is little or no agreement on the key drivers of a system, the
extent of the relationship, how best to represent them or their probability distributions
[@conradt2024; @lempert2013]. Exploratory modelling embraces uncertainty as an inherent
characteristic of complex environmental systems [@lempert2010; @lempert2013] and is a core
methodology underpinning the development of robust and adaptive management strategies
[@haasnoot2013].

>>>>

An exploratory scenario modelling approach was adopted for this investigation. The method
involves exploring a wide range of potential futures under different assumptions of
environmental (climatic) and ecological conditions. Exploratory modelling approaches have
gained favour in recent years to explore the implications of deep uncertainty; where there
is little or no agreement on the key drivers of a system, the extent of the relationship,
how best to represent them or their probability distributions [@conradt2024; @lempert2013].
The approach embraces uncertainty as an inherent characteristic of complex environmental
systems [@lempert2010; @lempert2013] and is a core methodology underpinning the development
of robust and adaptive management strategies [@haasnoot2013].
